---
title: "Module 12"
author: "Robert Black"
date: "2025-11-16"
output: html_document
---

## Introduction

R Markdown is a simple way to combine text, code, and results in a single document. It lets you write reports that include formatted text, math, and live R code.

## What is R Markdown?

R Markdown uses Markdown syntax for formatting and lets you embed R code chunks. When you knit the document, the code runs and the results appear in the output.

## At least one LaTeX math expression: 
Inline Expression  $\alpha + \beta = \gamma$.

And a displayed equation:
$$
E = mc^2
$$

## At least two executable R code chunks that part 1

Show a summary

```{r}
data(mtcars)
summary(mtcars)
```

## At least two executable R code chunks that part 2

Show a plot

```{r}
library(ggplot2)
ggplot(mtcars, aes(x=wt, y=mpg)) + geom_point() + theme_minimal()
```

## Reflection

Using R Markdown makes displaying reports and other information much easier and quicker than writing plain reports. The biggest advantage of R Markdown is the efficiency and speed gained when creating reports with this method. However, if your requirements call for more control over webpage design, R Markdown may not be the best option, as it does not offer enough features for advanced design modifications.
---

*Tip: If something looks odd, check your chunk options and Markdown formatting. Preview often!*
